Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-23 paper.tex
Addresses point 4 in review #25B

    It is instructive to compare the partially reliable send and receive
    functions to their Berkeley Sockets API counterparts. The
    \texttt{send\_message()} call takes four additional parameters. These are 1)
    a message sequence number, that can be used to re-order messages and detect
    message loss; 2) a relative deadline, which is combined with an estimate of
    the current round-trip-time, and the time that the message has spent in the
    sending buffer, to determine if a message will arrive in time to be
    played-out; 3) the message sequence number of any message on which this
    depends, for example, of a video I-frame on which a P-frame is predicted;
    and 4) a sub-stream identifier, used, for example, to differentiate audio,
    video, sub-title, control, and repair streams.

    The \texttt{recv\_message()} call returns the sequence number, dependency
    information, and sub-stream identifier along with any received message.
    This allows the receiver to direct the message to the correct decoding queue.

>>>>

    It is instructive to compare the partially reliable send and receive
    functions to their Berkeley Sockets API counterparts. The
    \texttt{send\_message()} call takes four additional parameters. These are 1)
    a message sequence number, that can be used to re-order messages and detect
    message loss; 2) a relative deadline, which is combined with an estimate of
    the current round-trip-time, and the time that the message has spent in the
    sending buffer, to determine if a message will arrive in time to be
    played-out; 3) the message sequence number of any message on which this
    depends, for example, of a video I-frame on which a P-frame is predicted;
    and 4) a sub-stream identifier, used, for example, to differentiate audio,
    video, sub-title, control, and repair streams. Of this metadata, only the
    sub-stream identifier is sent on the wire. The sequence number, deadline,
    and dependency information is used only by the sender to provide the
    partially reliable service.

    The \texttt{recv\_message()} call returns the sub-stream identifier and
    length of the message, along with the received message data. This allows 
    the receiver to direct the message to the correct decoding queue.
